Verifying Demonstrations

### 2021-06-16 paper/related-work.tex
Updates relatd-work.tex with broken out parts

Our scheme relates to several other works: the crowd counting methods and 
location proof systems already described in \cref{current-crowd-counting}, and 
Sybil-free pseudonym systems.

Our Sybil-free pseudonym system is very similar to that of 
\textcite{SybilFreePseudonyms}.
Both are based on the work of \textcite{HowToWinTheCloneWars}.
We make the same simplification of~\cite{HowToWinTheCloneWars} as 
\textcite{SybilFreePseudonyms}, but we also require an interactive version.
Furthermore, our \acp{PK} must be distance bounding.

>>>>

Our scheme relates to several other works: crowd counting methods, location 
proof systems, and Sybil-free pseudonym systems.

\input{current-crowd-counting}
\input{location-proof-systems}
\input{sybil-free-systems}
